Ae. albopictus CPP manuscript

### 2019-11-01 MS.Rmd
methods updates

```{r eval=FALSE, message=FALSE, include=FALSE}
install.packages("tidyverse") #1.2.1
install.packages("drc") #3.0.1
install.packages("stringr")
install.packages("geosphere")
install.packages("lubridate")
install.packages(c("maps", "mapdata"))
devtools::install_github("dkahle/ggmap")
install.packages("scatterpie")
install.packages("ggedit")
install.packages("ggrepel")
install.packages("cowplot")
```

>>>>

```{r eval=FALSE, message=FALSE, include=FALSE}
install.packages("tidyverse") #1.2.1
install.packages("drc") #3.0.1
install.packages("stringr")
install.packages("geosphere")
install.packages("lubridate")
install.packages(c("maps", "mapdata"))
devtools::install_github("dkahle/ggmap")
install.packages("scatterpie")
install.packages("ggedit")
install.packages("ggrepel")
install.packages("papeR")
install.packages("cowplot")
